---
title: "Analysis of MEB COVID Survey 2"
author: "MEB Team"
date: "16 Nov 2021"
output: pdf_document
---

\Large Note: Will explain later

\newpage
\tableofcontents 


```{r setup, include=FALSE} 
knitr::opts_chunk$set(echo = FALSE)

library(cowplot)
library(tidyverse)
library(ggplot2)
library(MASS)
library(ggrepel)
library(RColorBrewer)
library(stargazer)
library(DeclareDesign)
library(texreg)
library(car)
library(lubridate)
library(scales)
library(cowplot)
library(writexl)
library(janitor)
library(gridExtra)
library(grid)
library(ggpubr)
```

```{r, include=FALSE}
#Import data

#PC import

#raw_dta <- read_csv("C:/Users/Aditya/Google Drive (aditya.unnikrishnan@cprindia.org)/State Capacity/Moral Economy Survey/COVID Short Survey/data_analysis_results/01_raw_data/meb_02102020.csv", col_names = FALSE)

#Mac import

raw_dta <- read_csv("meb2data_23nov.csv.csv", col_names = FALSE)
```

```{r, include=FALSE}
#Clean up: deleting extra columns, merging the state related questions, deleting the old state columns, removing all incomplete answers, adding two filters to ensure only responses by currently serving IAS officers
processed_dta<-raw_dta[-c(1,2),-c(2, 5:9,15,140,141)]%>%
unite('Merged1', X19:X55, remove=FALSE, na.rm=TRUE) %>%
  unite('Merged2', X56:X92, remove = FALSE, na.rm=TRUE) %>%
  unite('Merged3',X93:X129, remove=FALSE, na.rm=TRUE)%>% 
  subset(select=-(X19:X55))%>%
  subset(select=-(X56:X92))%>%
  subset(select=-(X93:X129))%>%
  #na.omit %>%
  filter(!is.na(X139))%>%
  filter(X10=="Yes") %>% 
 separate(Merged1, c('Merged1.1', 'Merged1.2'), sep = "([_])") %>% 
 separate(Merged2, c('Merged2.1', 'Merged2.2'), sep = "([_])") 
```

```{r, include=FALSE}
#Checking for outliers 
#Batch outliers
hist(as.numeric(raw_dta$X11), col="#ccf5ff", border=F, xlab="Year of Joining", ylab = "Frequency", main= "Distribution of IAS Batches")
#None

#Respondents who sped through the survey (min time = 3 minutes)
processed_dta$time_spent<-mdy_hms(processed_dta$X4, tz="Asia/Kolkata")- mdy_hms(processed_dta$X3, tz="Asia/Kolkata")
processed_dta<-processed_dta %>%
  mutate(speeders=ifelse(time_spent<3, 1, 0)) 
#Decided not to exclude anyone on this basis

#The number of NA responses for each question in the processed data
processed_dta %>% 
  dplyr::select(everything()) %>% 
  summarise_all(funs(sum(is.na(.))))
#Column X136 has 69 NAs, all others have zero.
```

```{r, include=FALSE}
#Define new theme 
newtheme <- theme_bw() +
  theme(panel.border = element_rect(color = "darkgrey", size = 2), 
        panel.grid.major = element_blank()
        )
```

```{r, include=FALSE}
#Recoding answer options from character strings to numeric values for the processed_dta 
#Q7 (X16) #Q8 (X17) #Q9 (X18) #Q13 (X130) #Q15 (X132)  #Q16 (X133) #Q17 (X134) #Q18 (X135) #20 (X137) #Q21 (X138) #Q22 (X139)
#Deleting Q19 (X136) as is since this is the error question 

processed_dta<-processed_dta %>% 
  mutate(X16 = ifelse(X16== "The second Covid-19 surge was expected and should have seen much more advance planning.", 1, 2)) %>% 
  mutate(X17 = ifelse(X17 =="Even proposals for advance planning received little purchase in the last one year.",1,
                      ifelse(X17 =="Planning got lost mid-way due to signals that we have managed the pandemic well.", 2,
                             ifelse(X17 == "Systematic advance planning has never been part of our ethos.", 3, 4)))) %>%
  mutate(X18 = ifelse(X18 == "Building health system preparedness was not adequately prioritised.",1,
                      ifelse(X18=="Health system preparedness increased but was overwhelmed by the unprecedented scale of the infection.", 2, 
                             ifelse(X18=="Health system preparedness increased substantially and performed adequately.", 3, 4)))) %>%                            
  mutate(X130 = ifelse(X130=="Resources and autonomy can always be generated if only the system were to positively acknowledge initiative and motivation as a rule.", 1, 2)) %>% 
  mutate(X131 =ifelse(X131=="Knowing the risks involved, such events should not have been scheduled at all.",1,
                      ifelse(X131=="The risks from these events were too high. They could have been managed better (perhaps by staggering the events or by curtailing participation).", 2,
                             ifelse(X131=="The surge was caused by a natural progression of the virus. Prohibiting these events would not have prevented this surge.", 3,4)))) %>% 
  mutate(X132 = ifelse(X132=="Given the lack of consensus in our democracy, any other course of action would have resulted in unnecessary chaos and confusion among the public.", 1, 2)) %>% 
  mutate (X133= ifelse (X133 == "During the pandemic, policy has exhibited a rational response to changing evidence and information about the pandemic.", 1, 
                      ifelse(X133 == "Even though the pandemic posed unique challenges, policy making could still be characterised as ad hoc, responding to political imperatives, public pressure and judicial pronouncements.", 2, 3))) %>%
  mutate (X134 = ifelse (X134 == "India has successfully followed this nationally laid down trajectory of vaccine implementation.", 1, 
                       ifelse(X134 == "Our vaccination efforts have been adequate in following this trajectory though some states could have done better.", 2, 
                              ifelse(X134 == "Our vaccination policy implementation has been less than satisfactory because of poor performance at state level.", 3, 4)))) %>% 
  mutate (X135 = ifelse (X135 == "We could at least use our networks to render some assistance at an individual level.", 1, 
                       ifelse(X135 == "We should have done so much more to improve the system when we had the time.", 2, 
                              ifelse(X135 == "We were as deprived and helpless as the ordinary citizen, in the face of this utter collapse of the health care system.", 3, 4)))) %>%
  mutate (X137 = ifelse (X137 == "The government’s fiscal situation did not permit such measures.", 1, 
                       ifelse(X137 == "The pandemic’s limited initial impact led to a view that mass vaccination would not be urgently required in India.", 2, 
                              ifelse(X137 == "The private sector in India does not inspire confidence.", 3, 4)))) %>% 
  mutate (X138 = ifelse (X138 == "Slightly agree", 1, 
                       ifelse(X138 == "Slightly disagree", 2, 
                              ifelse(X138 == "Strongly agree", 3, 4)))) %>%
  mutate (X139 = ifelse (X139 == "By focussing on failures in pandemic management, the media has exaggerated the sense of failure and despair.", 1, 
                       ifelse(X139 == "The media has failed to capture the full scale and intensity of the disaster.", 2, 3))) %>% 
  dplyr::select(-X136)
```


```{r, include=FALSE}
#Data Wrangling
set.seed(24102020)
#Creating a dataset of currently serving officers with columns indicating (1) the allocated state (2) their SDG classification and (3) the age of the officers

#Need to check and add the exact distribution of officers in the states and UT for combined cadres
#Question for Aditya: how did the sample function work last time? 
full_serving <- processed_dta %>% 
  filter(X13=="Yes, currently serving") 

full_serving <- full_serving %>% 
  mutate(state = ifelse(X12=="Assam Meghalaya", sample(c("Assam", "Meghalaya"), prob = c(0.69, 0.31), size = length(which(full_serving$X12=="Assam Meghalaya")), replace = TRUE),
                       ifelse(X12=="AGMUT", sample(c("Delhi", "Arunachal Pradesh",  "Mizoram","Goa", "DNH and DD","Chandigarh", "Andaman and Nicobar Islands", "Lakshadweep Islands", "Puducherry"), prob = c(0.36, 0.18, 0.14, 0.09, 0.05, 0.05,0.05, 0.05, 0.5), size = length(which(full_serving$X12=="AGMUT")), replace = TRUE), X12))) %>% 
   mutate(sdg = ifelse(state== "Uttar Pradesh" | state=="Bihar" | state =="Assam", "Aspirant", 
                       ifelse(state=="Puducherry"|state=="Tamil Nadu"| state=="Chandigarh"| state=="Himachal Pradesh"|state=="Kerala", "Frontrunner", "Performer"))) %>% 
   mutate(age = ifelse(X11>2011, "2012 and after", "2011 and before"))


#Creating a dataset of former IAS officers and adding the same three columns as above to help with merging the two datasets 
full_former<-processed_dta %>% 
  filter(X13=="No, I am a former IAS officer") %>% 
  mutate(state = NA) %>% #state and sdg are kept NA for now. However we can make these allocations if needed 
  mutate(sdg = NA) %>% 
  mutate(age ="Former officer")
```

```{r}
#Creating subsets

#SDG subsets
#Dataset of aspirant states 
fullsdg_aspirant <- full_serving %>% 
  filter(sdg == "Aspirant") #46 observations 

#Dataset of performer states
fullsdg_performer <- full_serving %>% 
  filter(sdg == "Performer") #313 observations

#Dataset of frontrunner states
fullsdg_frunner <- full_serving %>% 
  filter(sdg == "Frontrunner") #65 observations 

#Age subsets
#Dataset of young officers
fullage_young <- full_serving %>% 
  filter(age == "2012 and after") #231

#Dataset with old officers
fullage_old <- full_serving %>% 
  filter(age == "2011 and before") #193

#Dataset of all respondents, former and currently serving with columns for state, sdg and age 
full_respondents<- full_serving %>% 
  add_row(full_former)
```

```{r, include=FALSE}
#Creating a dataset with the averages for each answer choice for all questions
#Used to check with Survey Monkey 
summary_nogroup<-full_serving %>% 
  dplyr::select(c(X16, X17, X18, X130, X131, X132, X133, X134, X135, X137, X138, X139)) %>% 
  summarise(X16ones=sum(X16==1)/length(X16), X16twos=sum(X16==2)/length(X16),
            X17ones=sum(X17==1)/length(X17), X17twos=sum(X17==2)/length(X17), X17threes=sum(X17==3)/length(X17), X17fours=sum(X17==4)/length(X17),
            X18ones=sum(X18==1)/length(X18), X18twos=sum(X18==2)/length(X18), X18threes=sum(X18==3)/length(X18), X18fours=sum(X18==4)/length(X18), 
            X130ones=sum(X130==1)/length(X130), X130twos=sum(X130==2)/length(X130),
            X131ones=sum(X131==1)/length(X131), X131twos=sum(X131==2)/length(X131), X131threes=sum(X131==3)/length(X131), X131fours=sum(X131==4)/length(X131), 
            X132ones=sum(X132==1)/length(X132), X132twos=sum(X132==2)/length(X132),
            X133ones=sum(X133==1)/length(X133), X133twos=sum(X133==2)/length(X133), X133threes=sum(X133==3)/length(X133),
            X134ones=sum(X134==1)/length(X134), X134twos=sum(X134==2)/length(X134), X134threes=sum(X134==3)/length(X134), X134fours=sum(X134==4)/length(X134), 
            X135ones=sum(X135==1)/length(X135), X135twos=sum(X135==2)/length(X135), X135threes=sum(X135==3)/length(X135), X135fours=sum(X135==4)/length(X135),
            X137ones=sum(X137==1)/length(X137), X137twos=sum(X137==2)/length(X137), X137threes=sum(X137==3)/length(X137), X137fours=sum(X137==4)/length(X137),
            X138ones=sum(X138==1)/length(X138), X138twos=sum(X138==2)/length(X138), X138threes=sum(X138==3)/length(X138), X138fours=sum(X138==4)/length(X138),
            X139ones=sum(X139==1)/length(X139), X139twos=sum(X139==2)/length(X139), X139threes=sum(X139==3)/length(X139))%>% 
  ungroup()
```

```{r, include=FALSE}
#Creating a dataset with the averages for each answer choice for all questions grouped by the state 
#Used for SDG comparison
summary_state<-full_serving %>% 
  dplyr::select(c(X16, X17, X18, X130, X131, X132, X133, X134, X135, X137, X138, X139, state)) %>% 
  group_by(state) %>% 
  summarise(X16ones=sum(X16==1)/length(state), X16twos=sum(X16==2)/length(state),
            X17ones=sum(X17==1)/length(state), X17twos=sum(X17==2)/length(state), X17threes=sum(X17==3)/length(state), X17fours=sum(X17==4)/length(state),
            X18ones=sum(X18==1)/length(state), X18twos=sum(X18==2)/length(state), X18threes=sum(X18==3)/length(state), X18fours=sum(X18==4)/length(state), 
            X130ones=sum(X130==1)/length(state), X130twos=sum(X130==2)/length(state),
            X131ones=sum(X131==1)/length(state), X131twos=sum(X131==2)/length(state), X131threes=sum(X131==3)/length(state), X131fours=sum(X131==4)/length(state), 
            X132ones=sum(X132==1)/length(state), X132twos=sum(X132==2)/length(state),
            X133ones=sum(X133==1)/length(state), X133twos=sum(X133==2)/length(state), X133threes=sum(X133==3)/length(state),
            X134ones=sum(X134==1)/length(state), X134twos=sum(X134==2)/length(state), X134threes=sum(X134==3)/length(state), X134fours=sum(X134==4)/length(state), 
            X135ones=sum(X135==1)/length(state), X135twos=sum(X135==2)/length(state), X135threes=sum(X135==3)/length(state), X135fours=sum(X135==4)/length(state),
            X137ones=sum(X137==1)/length(state), X137twos=sum(X137==2)/length(state), X137threes=sum(X137==3)/length(state), X137fours=sum(X137==4)/length(state),
            X138ones=sum(X138==1)/length(state), X138twos=sum(X138==2)/length(state), X138threes=sum(X138==3)/length(state), X138fours=sum(X138==4)/length(state),
            X139ones=sum(X139==1)/length(state), X139twos=sum(X139==2)/length(state), X139threes=sum(X139==3)/length(state)) %>% 
  ungroup()
```

```{r}
#Creating a dataset with the averages for each answer choice for all questions grouped by the cadre
summary_cadre<-full_serving %>% 
  dplyr::select(c(X16, X17, X18, X130, X131, X132, X133, X134, X135, X137, X138, X139, X12)) %>% 
  group_by(X12) %>% 
  summarise(X16ones=sum(X16==1)/length(X12), X16twos=sum(X16==2)/length(X12),
            X17ones=sum(X17==1)/length(X12), X17twos=sum(X17==2)/length(X12), X17threes=sum(X17==3)/length(X12), X17fours=sum(X17==4)/length(X12),
            X18ones=sum(X18==1)/length(X12), X18twos=sum(X18==2)/length(X12), X18threes=sum(X18==3)/length(X12), X18fours=sum(X18==4)/length(X12), 
            X130ones=sum(X130==1)/length(X12), X130twos=sum(X130==2)/length(X12),
            X131ones=sum(X131==1)/length(X12), X131twos=sum(X131==2)/length(X12), X131threes=sum(X131==3)/length(X12), X131fours=sum(X131==4)/length(X12), 
            X132ones=sum(X132==1)/length(X12), X132twos=sum(X132==2)/length(X12),
            X133ones=sum(X133==1)/length(X12), X133twos=sum(X133==2)/length(X12), X133threes=sum(X133==3)/length(X12),
            X134ones=sum(X134==1)/length(X12), X134twos=sum(X134==2)/length(X12), X134threes=sum(X134==3)/length(X12), X134fours=sum(X134==4)/length(X12), 
            X135ones=sum(X135==1)/length(X12), X135twos=sum(X135==2)/length(X12), X135threes=sum(X135==3)/length(X12), X135fours=sum(X135==4)/length(X12),
            X137ones=sum(X137==1)/length(X12), X137twos=sum(X137==2)/length(X12), X137threes=sum(X137==3)/length(X12), X137fours=sum(X137==4)/length(X12),
            X138ones=sum(X138==1)/length(X12), X138twos=sum(X138==2)/length(X12), X138threes=sum(X138==3)/length(X12), X138fours=sum(X138==4)/length(X12),
            X139ones=sum(X139==1)/length(X12), X139twos=sum(X139==2)/length(X12), X139threes=sum(X139==3)/length(X12)) %>% 
  ungroup() %>% 
  rename(cadre = "X12")
 
```

Example graph I: Question 7, X16 (binary answers)
```{r}
##Gurkirat##
#Example graph for question 7. I have used Arithmetic Mean instead of Weighted Mean.
q7full_mean_ones <- round(mean(summary_cadre$X16ones)*100,2) #consider doing rounding and mean estimation at an earlier stage for all questions.
q7full_mean_twos <- round(mean(summary_cadre$X16twos)*100,2)
q7full_plot <- c(q7full_mean_ones, q7full_mean_twos) 
q7full_plot_labels <- c("The second Covid-19 surge was expected.", "The second Covid-19 surge was unprecedented.") 
q7full_plot_dta <- data.frame(q7full_plot, q7full_plot_labels) 
q7full_plot <- ggplot(q7full_plot_dta, aes(x=q7full_plot_labels, y=q7full_plot, fill = q7full_plot_labels)) +
  geom_bar(stat="identity", width= 0.5, show.legend = FALSE) + 
  geom_text(aes(label=scales::percent(q7full_plot/100)), vjust=-0.3, size=3.5) +
  scale_y_continuous(limits = c(0,100)) +  
  scale_fill_brewer(palette="YlGnBu") +
  labs(x="",y="Percent") +
  newtheme

q7full_plot

##Gurkirat##
```

Example graph II: Question 21, X138 (4 responses)
```{r}
##Gurkirat##
#Example graph for question 21. I have used Arithmetic Mean instead of Weighted Mean.

q21full_mean_ones <- round(mean(summary_cadre$X138ones)*100,3) #consider doing rounding and mean estimation at an earlier stage for all questions.
q21full_mean_twos <- round(mean(summary_cadre$X138twos)*100,3) 
q21full_mean_threes <- round(mean(summary_cadre$X138threes)*100,3)
q21full_mean_fours <- round(mean(summary_cadre$X138fours)*100,3)
q21full_plot <- c(q21full_mean_ones, q21full_mean_twos, q21full_mean_threes, q21full_mean_fours) 
q21full_plot_labels <- c("Slightly agree", "Slightly disagree", "Strongly agree", "Strongly disagree") 
q21full_plot_dta <- data.frame(q21full_plot, q21full_plot_labels) 
q21full_plot <- ggplot(q21full_plot_dta, aes(x=q21full_plot_labels, y=q21full_plot, fill = q21full_plot_labels)) +
  geom_bar(stat="identity", width= 0.5, show.legend = FALSE) + 
  geom_text(aes(label=scales::percent(q21full_plot/100)), vjust=-0.3, size=3.5) +
  scale_y_continuous(limits = c(0,100)) +  
  scale_fill_brewer(palette="YlGnBu") +
  labs(x="",y="Percent") +
  newtheme

q21full_plot

##Gurkirat##

```

#Rahul says: 
#folks, the cadre wise dataset and example graphs look great. Next week, spend some time thinking about whether you want to improve the graph code we had written for the previous survey in any way. 
#next steps: 
#adding the weight by cadre - here my recommendation is not to do any manual addition of weights like we did last time. Rather, create a column of the number of officers by cadre from the TCPD population data. Merge that column with the cadre dataset. Then create a new column called weight = number_pop/sum(number_pop). 
#creating a very simple dataset of final weighted responses for the full graphs. This should ideally have just one row with all the weighted averages and multiple columns for the responses. 
#Replicate the graphs rather quickly (should be easy) for the full graphs. 

#Pending decision - on weighting age. Let's chat about this Monday once we know the pop numbers. 


```{r, include=FALSE}
#Testing graphs
##Shubhangi##
X17_plot_means<-summary_cadre %>% 
  dplyr::select(cadre, X17ones, X17twos, X17threes, X17fours) %>% 
  mutate_if(is.numeric, ~ . * 100) %>% 
  mutate_if(is.numeric, round,2) %>% 
  bind_rows(summarise_all(.,~ if(is.numeric(.)) mean(.) else("Total"))) %>% 
  slice_tail() %>% 
  dplyr::select(-cadre) %>% 
  unlist()

X17_plot_labels<-c("Advance planning received little purchase in last 1 year", "Planning got lost due to signals that we have managed pandemic", "Advance planning has never been part of our ethos", "We took adequate measures to plan our responses") #labels are too long, will edit these later 
X17_plot_dta <- data.frame(X17_plot_means, X17_plot_labels)

X17_plot <- ggplot(X17_plot_dta, aes(x=X17_plot_labels, y=X17_plot_means, fill = X17_plot_labels)) +
  geom_bar(stat="identity", width=0.5, show.legend = FALSE, fill=c("#fecc5c","#fd8d3c","#ffffb2",   "#e31a1c")) + 
  geom_text(aes(label=scales::percent(X17_plot_means/100)), vjust=-0.3, size=3.5) +
  scale_y_continuous(limits = c(0,100)) +  
  labs(x="",y="Percent") +
  newtheme
  ##Shubhangi##
```

```{r, include=FALSE}
##Shubhangi##
#Creating a column of weights for states within each SDG tier 
#This code requires three different datasets: the summary_state (mean averages for each answer choice), ias_processed_dta (distribution of IAS officers by state and age) and full_serving (since it has a column denoting the SDG tiers) 
summary_state_analysis <- summary_state %>% 
  mutate(sdg_weight = ifelse(state== "Uttar Pradesh" | state == "Bihar" | state =="Assam", ias_processed_dta$total/sum(full_serving$sdg=="Aspirant"), 
                             ifelse(state=="Puducherry"|state=="Tamil Nadu"|state=="Kerala"|state=="Himachal Pradesh"|state=="Chandigarh", ias_processed_dta$total/sum(full_serving$sdg=="Frontrunner"), ias_processed_dta$total/sum(full_serving$sdg=="Performer"))))
##Shubhangi##
```


```{r, include=FALSE}
##Gurkirat##
#Adding state weights and age weights, and then transferring them from "ias_processed_dta" to "summary_state_analysis"

#Note: I had to combine two data frames (subset of ias_processed_dta & summary_state_analysis) because it is not  possible to execute dplyr commands with multiple data frames particularly when the row size is different across data frames ("Andaman and Nicobar Islands" and "Lakshadweep Islands" in IAS grouped data). It was rendering an error when I tried doing the analysis in a single data frame. (not the case with "ifelse")

ias_processed_dta <- ias_processed_dta %>% 
mutate (state_weight = total/sum(total)) %>% 
mutate(age_weight_old = pre2012/sum(pre2012)) %>% 
mutate(age_weight_young = post2012/sum(post2012)) 

ias_processed_dta1 <- ias_processed_dta %>% 
dplyr:: select (State, age_weight_old, age_weight_young, state_weight) %>% 
subset(State !="Andaman and Nicobar Islands" & State !="Lakshadweep Islands" & State !="Total")

summary_state_analysis <- cbind (summary_state_analysis, ias_processed_dta1)

summary_state_analysis <- summary_state_analysis %>% 
dplyr :: select (-State)

##Gurkirat##

```
